---
title: "Assignment 1-3: Data display, logistic regression, and propensity score analysis for Question 1.1"
author: "Your Name"
date: "Today's date"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Due Sunday, February 11, 2024 @ midnight through Github**

Improve your data display, improve your logistic regression, and fit a propensity score analysis to using the NMES data to answer:

**Question 1.1: How does the risk of disease compare for smokers and otherwise similar non-smokers?**

You will want to think about what variables will be important to look at for examining the risk of disease for smokers and otherwise similar non-smokers, and then what kind of visual display would be good to illustrate this relationship. 

You should complete this assignment in this .Rmd file.  Any text you want to include should be written outside of the code chunks.  Any code must be written inside of the code chunks.

When you want to test and run your whole assignment, you can click the "Knit" button to create an HTML document with your work.

All code to create your data display and fit your logistic regression must be included in this document for it to knit properly.  That is, this document is a stand-alone document that shows all of the data analysis steps starting with the raw data.  It's helpful to periodically knit your document as you work to be sure you've included all the necessary code.

**Do the following things: **

1. Read in the NMES data set and store it into an object called `nmes_data`.  (Note, in this project the data is in the main project directory, so the path to the data is just the file name itself.)
```{r}
library(tidyverse)
nmes_data <- read_csv("nmesUNPROC.csv")
```

2. If you want to recode any of the variables in the data set, as we did in the class notes, you can do that in the code chunk here:
```{r}
### put recoding data here
### you can use comments like this to describe what you are doing

```

3. Include the code needed to make your updated data display here.  While working on your assignment, you might try lots of different things.  Please only include the code for the final display that you are submitting for your assignment below (delete the other things you have tried).
```{r}
### put code to create data display here

```

4. Write a couple of sentences interpreting your display in context of the question of interest:

Write your text here.

5. Include an updated final multivariable logistic regression model to address question the question and interpret the results.

```{r}
# code for logistic regression

```

Write your interpretation text here.

6. Perform a propensity score analysis to address the question and interpret the results.  

First, use logistic regression to estimate propensity scores for the treatment of smoking (`eversmk`); that is, use logistic regression to estimate the probability of smoking given possible confounding variables.

```{r}
# code for calculating propensity scores

```

Next create propensity score quintile groups using the predicted probabilities from the logistic regression model for predicting smoking status.

```{r}
# code for creating propensity score quintiles

```

Finally, use logistic regression with quintiles of your propensity scores to answer the question of interest.

```{r}
# code for logistic regression

```

Interpret your results here

6. When you are ready to submit, post a screenshot of your multivariable logistic regression results and your propensity score results, on Piazza in the "Assignment 1-3 Results" thread. Include your interpretations of what these two models say about Question 1.1 and any thoughts you have on which of these two analysis methods is preferred for answering Question 1.1.

7. When you are ready to submit your assignment on Github, do ALL of the following:

* First, knit your .Rmd file to see if it will compile.  If it doesn't knit, you can still follow the steps below to submit your assignment, but please try to resolve the knitting issues before you submit.  You can reach out to use at phbiostats@jhu.edu for help!
* Next you need to **commit** the changes you've made to the document.  Click the colorful Git button at the top of the RStudio window and select "Commit" from the menu.
* In the window that opens, **stage** your changes by clicking the check boxes next to the `Asst1-3.Rmd` file.
* In the "Commit message" box, type a short description of what changes you've made, something like: `Completed assignment`
* Click the "Commit" button on the bottom right.
* You'll see a window that will tell you about the changes that you've made.  Click "Close" to close the window.  You've successfully committed! You can close this commit window now.
* After committing, you must **push** your changes to the repository on Github.  Do this by clicking the colorful Git button again and select "Push Branch".  
* Again, you'll see a window open that tells you your changes have been pushed!
* If you want, you can look at your repository on [Github.com](https://github.com/) and should be able to see your changes there!  
* You've successfully submitted your assignment :)


